### 2013-11-28 paper/main.tex
added some tikz diagrams, still a work in progress

\usepackage{url}
\usepackage{hyperref}
\usepackage{graphicx}
%\usepackage{multicol}
\usepackage{nonfloat}
\usepackage{amsmath}
\usepackage{mathtools}
\usepackage{parskip}

@@

\begin{figure}[hbp!]
\begin{center}
\includegraphics[scale=0.6]{img/schematic-linear_engine_model-ed1}
\end{center}
\caption{Linear engine model.}\label{fig:lem}
\end{figure}

@@

This model has one complication that makes it difficult to use compared
to typical elementary control systems.
All the inputs and outputs are specified as deltas ($\Delta$).
The torque input, for example, cannot be given as a constant ($T$) because this
actually means $\Delta T$

@@

\clearpage
\begin{figure}[!htbp]
\begin{center}
\includegraphics[scale=0.6]{img/schematic-control-ed1}
\end{center}
\caption{Simple feedback controller for inputs.
The gain can be used to slow down the input changes.
The output is an accumulation of all the step inputs.}
\label{fig:scont}
\end{figure}

@@

>>>>

\usepackage{url}
\usepackage{hyperref}
\usepackage{graphicx}
%\usepackage{multicol}
\usepackage{nonfloat}
\usepackage{amsmath}
\usepackage{mathtools}
\usepackage{parskip}
\usepackage{bloques}

\usepackage{tikz}
\usetikzlibrary{calc,arrows,positioning}
% control system tikz objects
\tikzset{shadow/.style={drop shadow={opacity=0.8},fill=white}}
\tikzset{sum/.style={circle,draw,very thick,shadow,minimum size=6mm}}
\tikzset{sumnp/.style={sum,
				label={{above left,xshift=1.0mm,yshift=-1.0mm}:$+$},
				label={{below left,xshift=1.0mm,yshift=1.0mm}:$-$}}}
\tikzset{sumxpxp/.style={sum,
				label={{above left,xshift=1.0mm,yshift=-1.0mm}:$+$},
				label={{above right,xshift=-1.0mm,yshift=-1.0mm}:$+$}}}
\tikzset{gain/.style={rectangle,draw,very thick,inner sep=2mm,shadow}}
%\newcommand{\nodesum}[2]{
%\node[sum]  (#1) [label={{above left,xshift=1.5mm,yshift=-1.5mm}:$+$},
%				  label={{below left,xshift=1.5mm,yshift=1.5mm}:$-$},#2] {};
%}

@@

\xdistance{1.8cm}
\ydistance{2.0cm}

\begin{figure}[hbp!]
\begin{center}
\begin{tikzpicture}
\bShadow
\bStart{$\Delta \text{control}$}
\bGain{$1.699$}
\bMinusF{S1}
\bGain{$\dfrac{8.5683}{z^2 - 0.9025 z}$}
\bMinusUp{$\Delta \text{torque}$}
\bGain{$\dfrac{2.98}{z - 0.9354}$}
\bGainFeedBack{$0.000093$}{S1}
\bEnd{$\Delta \text{rpm}$}
\end{tikzpicture}
\end{center}
\caption{Linear engine model.}\label{fig:lem}
\end{figure}

@@

This model has one complication that makes it difficult to use compared
to typical control systems.
All the inputs and outputs are specified as deltas ($\Delta$).
The torque input, for example, cannot be given as a constant ($T$) because this
actually means $\Delta T$

@@

\clearpage
\begin{figure}[!htbp]
\begin{center}

\begin{tikzpicture}
%\xdistance{1.2cm}
%\ydistance{1.5cm}
\bShadow
\bStart{$X$}
\bGain{$1 - z^{-1}$}
\bEnd{$\Delta X$}
\end{tikzpicture}

%\begin{tikzpicture}
%\xdistance{1.2cm}
%\ydistance{1.5cm}
%\bShadow
%\bStart{$X$}
%\bMinusF{S1}
%\bGain{$\Sigma$}
%\bFeedBack{}{S1}
%\bEnd{$\Delta X$}
%\end{tikzpicture}

\end{center}
\caption{$Z$ transform used to accumulate the input and convert
a steady state input to delta output.
See Appendix \ref{app:cdelta} for the derivation.}
\label{fig:scont}
\end{figure}

@@

% {{{ Steady State to Delta $Z$ Transform Derivation
\section{Steady State to Delta $Z$ Transform Derivation}
\label{app:cdelta}

\begin{figure}
\begin{center}

\begin{tikzpicture}[>=triangle 60,
	node distance=14mm, auto]
%	[inner sep=10mm, minimum size=6mm, node distance=20mm]

	\node[sumnp]  (sum1)	[] 					{};
	\node[sumxpxp] (sum2)	[below=of sum1] 	{};
	\node[gain] (gain1)		[right=of sum2]		{$z^{-1}$};
	\node[gain] (gain2)		[left=of sum2]		{$z^{-1}$};

	\draw [->] (sum2.north) -- 					(sum1.south);
	\draw [->] (gain1.west) -- node[below]{$v$} 	(sum2.east);
	\draw [->] (gain2.east) -- node[below]{$q$} 	(sum2.west);

	 \draw [->]
	 		($ (sum1.south) - (0,7mm) $)
			-- ++(-35mm,0) node[below left]{$r$} 
			|- (gain2.west);
	\draw [->]
			(-45mm,0) node[above] {$u$} to (sum1);
	\draw [->]
			(sum1) to (45mm,0) node[above] {$y$};
	\draw [->]
			($(sum1.east) + (33mm,0) $)
			|- (gain1);

\end{tikzpicture}

%\tikzstyle{block}=[draw,minimum size=2.4em]
%
%\tikzstyle{sum}=[draw,circle,minimum size=1.2em]
%
%%\tikzstyle{init} = [pin edge={to-,thin,black}]
%\begin{tikzpicture}[node distance=2.0cm,auto,>=latex']
%
%	% place all the block, points, relative to each other
%	\node [coordinate,node distance=2cm] (u) {u};
%	\node [block,right of=u] (k) {$K$};
%
%	\node [sum,right of=k] (s) {};
%
%	\node [coordinate,below of=s] (ds) {ds};
%	\node [block,right of=ds] (d) {$D(s)$};
%	\node [block,right of=s] (g) {$G(s)$};
%	\node [coordinate,right of=g] (gdy) {};
%	\node [coordinate,right of=gdy,node distance=2cm] (y) {y};
%	\node [coordinate,right of=d] (gd) {gd};
%
%	% add signs to sum
%	\node [left of=s,node distance=0cm,xshift=-3mm,yshift=3mm] {$+$};
%	\node [left of=s,node distance=0cm,xshift=-3mm,yshift=-4mm] {$-$};
%
%	% add labels to G(s) and D(s)
%	\node [right of=g,node distance=0cm,xshift=8mm,yshift=6mm] {$\dfrac{B}{A}$};
%	\node [right of=d,node distance=0cm,xshift=8mm,yshift=6mm] {$\dfrac{\beta}{\alpha}$};
%
%	% connect all the nodes and points
%	\path[->] (u) edge node {$u$} (k);
%	\path[->] (k) edge node {} (s);
%	\path[->] (ds) edge node {} (s);
%	\path[-]  (d) edge node {} (ds);
%	\path[->] (s) edge node {$\epsilon$} (g);
%	\path[-] (g) edge node {} (gdy);
%	\path[->] (gdy) edge node {$y$} (y);
%	\path[-] (gdy) edge node {} (gd);
%	\path[->] (gd) edge node {} (d);
%
%\end{tikzpicture}

\end{center}

\caption{System to accumulate values to convert a steady state
input to a delta output.}
\end{figure}
